Study on the effectiveness of the investment strategy based on a classifier with rules adapted by machine learning

### 2013-09-28 Article/Article20130912/LatexArt/tewi-paper-template.tex
fixed: equations

\subsection{Conditions of opening}
As mentioned before, the signal to open the position is the intersection of the current price of the observed value and some barrier (that results from the calculated band). Special parameter called the buffer (p5) has been added, causing the offset of barrier from its actual value. Thus, the condition for opening TewiMIC strategy is: 
\begin{equation}
\begin{split}
if[(price < bottomBorder(p1) - buffor(p5)) \\ 
and (current p6 < p6) and (Vol - meanVol(p7) < p8)] \\
then open position long
\end{split}
\end{equation}
where:\\
\textit{price} – current value for EURUSD;\\
\textit{bottomBorder(p1)} – value of lower band barrier for parameter p1; here minimum of last p1 minima; \\
\textit{buffor(p5)} – value of buffer that moves said barrier;\\
\textit{current p6} – number of currently opened positions;\\
\textit{Vol} – current value of volume (in the candle);\\
\textit{meanVol(p7)} – mean of volume of last p7 candles;\\

\noindent and the opening condition for TewiMiD is:
\begin{equation}
\begin{split}
if[(price < bottomBorder(p1) - buffor(p5)) \\ 
and (current p6 < p6) and (Vol - meanVol(p7) > p8)] \\
then open position short
\end{split}
\end{equation}

@@

\item Position will be closed if inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
\begin{equation}
(PriceO(i+k)-Price(i) )>-SL and (LowPrice(i+k)-Price(i))<-SL
\end{equation} 
Then the profit (in this case loss) will be calculated as:
\begin{equation}
Profit =-SL;
\end{equation}

@@

\item Position will be closed if inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
\begin{equation}
(PriceO(i+k)-Price(i) )<TP and (HighPrice(i+k)-Price(i))>TP
\end{equation} 
Then the profit will be calculated as:
\begin{equation}
Profit =TP;
\end{equation}
where \textit{HighPrice(i+k)} is the maximum value for (i+k) candle;

@@

\item Position will be closed if inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met:
\begin{equation}
(-PriceO (i+k)+price(i) )>-SL and (-HighPrice(i+k)+Price(i))<-SL
\end{equation}                          
Then the profit (in this case loss) will be calculated as:
\begin{equation}
Profit =-SL; 
\end{equation}

@@

\item Position will be closed if inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
\begin{equation}
(-PriceO(i+k)+price(i) )<TP and (-LowPrice(i+k)+Price(i))>TP
\end{equation}
Then the profit will be calculated as:
\begin{equation}
Profit =TP; 
\end{equation}

>>>>

\subsection{Conditions of opening}
As mentioned before, the signal to open the position is the intersection of the current price of the observed value and some barrier (that results from the calculated band). Special parameter called the buffer (p5) has been added, causing the offset of barrier from its actual value. Thus, the condition for opening TewiMIC strategy is: 
\begin{equation}
\begin{split}
if[(price < bottomBorder(p1) - buffor(p5)) \\ 
and (current p6 < p6) and (Vol - meanVol(p7) < p8)] \\
\text{then open position long}
\end{split}
\end{equation}
where:\\
\textit{price} – current value for EURUSD;\\
\textit{bottomBorder(p1)} – value of lower band barrier for parameter p1; here minimum of last p1 minima; \\
\textit{buffor(p5)} – value of buffer that moves said barrier;\\
\textit{current p6} – number of currently opened positions;\\
\textit{Vol} – current value of volume (in the candle);\\
\textit{meanVol(p7)} – mean of volume of last p7 candles;\\

\noindent and the opening condition for TewiMiD is:
\begin{equation}
\begin{split}
if[(price < bottomBorder(p1) - buffor(p5)) \\ 
and (current p6 < p6) and (Vol - meanVol(p7) > p8)] \\
\text{then open position short}
\end{split}
\end{equation}

@@

\item Position will be closed if inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
\begin{equation}
(PriceO(i+k)-Price(i) )>-SL \text{ and } (LowPrice(i+k)-Price(i))<-SL
\end{equation} 
Then the profit (in this case loss) will be calculated as:
\begin{equation}
Profit =-SL;
\end{equation}

@@

\item Position will be closed if inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
\begin{equation}
(PriceO(i+k)-Price(i) )<TP \text{ and } (HighPrice(i+k)-Price(i))>TP
\end{equation} 
Then the profit will be calculated as:
\begin{equation}
Profit =TP;
\end{equation}
where \textit{HighPrice(i+k)} is the maximum value for (i+k) candle;

@@

\item Position will be closed if inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met:
\begin{equation}
(-PriceO (i+k)+price(i) )>-SL \text{ and } (-HighPrice(i+k)+Price(i))<-SL
\end{equation}                          
Then the profit (in this case loss) will be calculated as:
\begin{equation}
Profit =-SL; 
\end{equation}

@@

\item Position will be closed if inside the opening of the next (i + k)-th - the candle after i-th candle, in which the position was opened, following condition is met: 
\begin{equation}
(-PriceO(i+k)+price(i) )<TP \text{ and } (-LowPrice(i+k)+Price(i))>TP
\end{equation}
Then the profit will be calculated as:
\begin{equation}
Profit =TP; 
\end{equation}
